\begin{frame}{Navigation in Mobile Robots}

Several applications of robotic system, such as rescue operation and patrolling, require robots be capable of navigating themselves to reach a goal position.

\bigskip

The objective of mobile robot navigation is to produce plans/policy which move a robot from its current position to a navigation goal, also assuring it won't crash against obstacles, or get lost in the process.

\end{frame}


\begin{frame}{Map-based Navigation}

Map-based navigation is the conventional approach of achieving the aforementioned objective. This approach consists of 

\begin{itemize}
   \item Self-localisation
   \item Path planning
   \item Mapping
\end{itemize}

\end{frame}


\begin{frame}{Deep Reinforcement Learning (DRL)}

Reinforcement learning method is defined as any effective way of solving \textbf{stochastic optimal control} problems such as those formulated as Markov decision processes (MDPs).

\bigskip

Dynamic programming (DP) is a class of solution methods of optimal control problems.

\bigskip

The combination of DP and artificial neural networks (ANNs) is termed as \textbf{neuro-dynamic programming} in control theory. Deep reinforcement learning (DRL) is the term used in the artificial intelligence literature.

\bigskip

ANN is used as an optimisable function approximator to overcome the DP's limitation called \textit{curse of dimensionality} which means computational requirements grow exponentially with the number of state variables.

\end{frame}
